---
title: "Benjamin Milks's BMI Calculator"
author: "Benjamin Milks"
date: "March 7, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is BMI?
Wiki explains BMI as, "The body mass index (BMI) or Quetelet index is a value derived from the mass (weight) and height of an individual. The BMI is defined as the body mass divided by the square of the body height, and is universally expressed in units of kg/m2, resulting from mass in kilograms and height in metres."

https://en.wikipedia.org/wiki/Body_mass_index

## What My App Does
The user will put in their height and weight and receive a plot with their bmi and 2 other celebrity BMIS.

## How to Use it
Type in your height and weight. Then hit submit and you are done.

## How it is calculated behind the scenes
```{r, echo=TRUE, warning=FALSE}
## Weight is in Kilograms and Height is in cm.
exampleweight <- 75
exampleheight <- 180
bmi <- (exampleweight*10000)/(exampleheight^2)
bmi
## For my app I then add in 2 other known bmis and produce a bargraph.
```



